---
title: "Dungeons and Dragons: HotDQ"
runtime: shiny
output: html_document
---

Basic character information (without equipment) for Dungeons and Dragons campaign Hoard of the Queen run by Fellgernon at roll20.net. More information [here](https://app.roll20.net/campaigns/details/497617/hotdq-by-fellgernon).

```{r 'charInfo', echo = FALSE}
## New char template
newChar <- data.frame(
    Name = NA,
    Race = NA,
    Class = NA,
    Str = NA,
    Dex = NA,
    Con = NA,
    Int = NA,
    Wis = NA,
    Cha = NA,
    P.Str = FALSE,
    P.Dex = FALSE,
    P.Con = FALSE,
    P.Int = FALSE,
    P.Wis = FALSE,
    P.Char = FALSE,
    MaxHP = NA,
    Speed = NA,
    AC = NA,
    ACunarmoured = NA,
    Lvl = 1,
    ProfBonus = 2,
    XP = 104,
    P.Acrobatics = "No",
    P.AnimalHandling = "No",
    P.Arcana = "No",
    P.Athletics = "No",
    P.Deception = "No",
    P.History = "No",
    P.Insight = "No",
    P.Intimidation = "No",
    P.Investigation = "No",
    P.Medicine = "No",
    P.Nature = "No",
    P.Perception = "No",
    P.Performance = "No",
    P.Persuasion = "No",
    P.Religion = "No",
    P.SleightOfHand = "No",
    P.Stealth = "No",
    P.Survival = "No",
    Gender = NA,
    Age = NA,
    Height = NA,
    Weight = NA,
    Eyes = NA,
    Hair = NA,
    Size = "M",
    Vision = NA,
    Language1 = NA,
    Language2 = NA,
    Language3 = NA,
    Language4 = NA,
    Language5 = NA,
    Language6 = NA,
    Alignment = NA,
    Background = NA,
    RacialTraits = NA,
    PersonalityTraits = NA,
    Ideals = NA,
    Bonds = NA,
    Flaws = NA,
    ArmourProficiencies = NA,
    WeaponProficiencies = NA,
    ToolProficienices = NA,
    CPieces = 0,
    SPieces = 0,
    EPieces = 0,
    GPieces = 0,
    PPieces = 0,
    SpellSaveDC = NA,
    SpellAttackMod = NA,
    Cantrip1 = NA,
    Cantrip2 = NA,
    Cantrip3 = NA,
    Cantrip4 = NA,
    Cantrip5 = NA,
    SpellSlotUsed1 = NA,
    SpellSlotMax1 = NA,
    SpellSlotUsed2 = NA,
    SpellSlotMax2 = NA,
    SpellSlotUsed3 = NA,
    SpellSlotMax3 = NA,
    SpellSlotUsed4 = NA,
    SpellSlotMax4 = NA,
    SpellSlotUsed5 = NA,
    SpellSlotMax5 = NA,
    SpellSlotUsed6 = NA,
    SpellSlotMax6 = NA,
    SpellSlotUsed7 = NA,
    SpellSlotMax7 = NA,
    SpellSlotUsed8 = NA,
    SpellSlotMax8 = NA,
    SpellSlotUsed9 = NA,
    SpellSlotMax9 = NA
)
```

```{r 'processCharsFun', echo = FALSE}
process.attribute <- function(attr, prof, bonus) {
    floor((attr - 10) / 2) + ifelse(prof, bonus, 0)
}
process.skill <- function(prof, mod, bonus) {
    10 + mod + ifelse(prof == "No", 0, ifelse(prof == "Yes", bonus, bonus * 2))
}
processChar <- function(char) {
    char <- data.frame(char,
        Str.Mod = floor((char$Str - 10) / 2),
        Dex.Mod = floor((char$Dex - 10) / 2),
        Con.Mod = floor((char$Con - 10) / 2),
        Int.Mod = floor((char$Int - 10) / 2),
        Wis.Mod = floor((char$Wis - 10) / 2),
        Cha.Mod = floor((char$Cha - 10) / 2),
        
        Str.Save = process.attribute(char$Str, char$P.Str, char$ProfBonus),
        Dex.Save = process.attribute(char$Dex, char$P.Dex, char$ProfBonus),
        Con.Save = process.attribute(char$Con, char$P.Con, char$ProfBonus),
        Int.Save = process.attribute(char$Int, char$P.Int, char$ProfBonus),
        Wis.Save = process.attribute(char$Wis, char$P.Wis, char$ProfBonus),
        Cha.Save = process.attribute(char$Cha, char$P.Cha, char$ProfBonus)
    )
    char <- data.frame(char,
        Acrobatics = process.skill(char$P.Acrobatics, char$Dex.Mod, char$ProfBonus),
        AnimalHandling = process.skill(char$P.AnimalHandling, char$Wis.Mod, char$ProfBonus),
        Arcana = process.skill(char$P.Arcana, char$Int.Mod, char$ProfBonus),
        Athletics = process.skill(char$P.Athletics, char$Str.Mod, char$ProfBonus),
        Deception = process.skill(char$P.Deception, char$Cha.Mod, char$ProfBonus),
        History = process.skill(char$P.History, char$Int.Mod, char$ProfBonus),
        Insight = process.skill(char$P.Insight, char$Wis.Mod, char$ProfBonus),
        Intimidation = process.skill(char$P.Intimidation, char$Cha.Mod, char$ProfBonus),
        Investigation = process.skill(char$P.Investigation, char$Int.Mod, char$ProfBonus),
        Medicine = process.skill(char$P.Medicine, char$Wis.Mod, char$ProfBonus),
        Nature = process.skill(char$P.Nature, char$Int.Mod, char$ProfBonus),
        Perception = process.skill(char$P.Perception, char$Wis.Mod, char$ProfBonus),
        Performance = process.skill(char$P.Performance, char$Cha.Mod, char$ProfBonus),
        Persuasion = process.skill(char$P.Persuasion, char$Cha.Mod, char$ProfBonus),
        Religion = process.skill(char$P.Religion, char$Int.Mod, char$ProfBonus),
        SleightOfHand = process.skill(char$P.SleightOfHand, char$Dex.Mod, char$ProfBonus),
        Stealth = process.skill(char$P.Stealth, char$Dex.Mod, char$ProfBonus),
        Survival = process.skill(char$P.Survival, char$Wis.Mod, char$ProfBonus),
        Wealth = char$CPieces / 100 + char$SPieces / 10 + char$GPieces + char$EPieces / 2 +  char$PPieces * 10
    )
}
```

```{r 'createChars', echo = FALSE}
## Input info
chars.raw <- list(
    Azula = data.frame(
        Name = "Azula",
        Race = "Human",
        Class = "Monk",
        Str = 10,
        Dex = 16,
        Con = 11,
        Int = 9,
        Wis = 15,
        Cha = 9,
        P.Str = FALSE,
        P.Dex = FALSE,
        P.Con = FALSE,
        P.Int = FALSE,
        P.Wis = FALSE,
        P.Char = FALSE,
        MaxHP = 8,
        Speed = 30,
        AC = 0,
        ACunarmoured = 15,
        Lvl = 1,
        ProfBonus = 2,
        XP = 104,
        P.Acrobatics = "Yes",
        P.AnimalHandling = "No",
        P.Arcana = "No",
        P.Athletics = "Yes",
        P.Deception = "No",
        P.History = "No",
        P.Insight = "No",
        P.Intimidation = "No",
        P.Investigation = "No",
        P.Medicine = "No",
        P.Nature = "No",
        P.Perception = "No",
        P.Performance = "No",
        P.Persuasion = "No",
        P.Religion = "No",
        P.SleightOfHand = "No",
        P.Stealth = "No",
        P.Survival = "No",
        Gender = "Female",
        Age = 26,
        Height = 1.81,
        Weight = 66,
        Eyes = "Green",
        Hair = "Brown",
        Size = "M",
        Vision = "Normal",
        Language1 = "Common",
        Language2 = "Dwarvish",
        Language3 = NA,
        Language4 = NA,
        Language5 = NA,
        Language6 = NA,
        Alignment = "LN",
        Background = "Soldier.",
        RacialTraits = "Damaran Human.",
        PersonalityTraits = "Crude sense of humor.
    I’m full of inspiring and cautionary tales from my 
    military experience relevant to almost every combat situation.",
        Ideals = "Live and Let Die.",
        Bonds = "Someone saved my life in the battlefield.",
        Flaws = "Little respect for unproven warriors.",
        ArmourProficiencies = "None",
        WeaponProficiencies = "Simple weapons & Shortswords",
        ToolProficienices = "Cartographer’s tools.",
        CPieces = 0,
        SPieces = 0,
        EPieces = 0,
        GPieces = 15,
        PPieces = 0,
        SpellSaveDC = NA,
        SpellAttackMod = NA,
        Cantrip1 = NA,
        Cantrip2 = NA,
        Cantrip3 = NA,
        Cantrip4 = NA,
        Cantrip5 = NA,
        SpellSlotUsed1 = NA,
        SpellSlotMax1 = NA,
        SpellSlotUsed2 = NA,
        SpellSlotMax2 = NA,
        SpellSlotUsed3 = NA,
        SpellSlotMax3 = NA,
        SpellSlotUsed4 = NA,
        SpellSlotMax4 = NA,
        SpellSlotUsed5 = NA,
        SpellSlotMax5 = NA,
        SpellSlotUsed6 = NA,
        SpellSlotMax6 = NA,
        SpellSlotUsed7 = NA,
        SpellSlotMax7 = NA,
        SpellSlotUsed8 = NA,
        SpellSlotMax8 = NA,
        SpellSlotUsed9 = NA,
        SpellSlotMax9 = NA
    ),
    Ignius = data.frame(
        Name = "Ignius",
        Race = "Tiefling",
        Class = "Bard",
        Str = 10,
        Dex = 15,
        Con = 13,
        Int = 14,
        Wis = 12,
        Cha = 18,
        P.Str = FALSE,
        P.Dex = TRUE,
        P.Con = FALSE,
        P.Int = FALSE,
        P.Wis = FALSE,
        P.Char = TRUE,
        MaxHP = 9,
        Speed = 30,
        AC = 13,
        ACunarmoured = 12,
        Lvl = 1,
        ProfBonus = 2,
        XP = 104,
        P.Acrobatics = "Yes",
        P.AnimalHandling = "No",
        P.Arcana = "No",
        P.Athletics = "No",
        P.Deception = "Yes",
        P.History = "No",
        P.Insight = "No",
        P.Intimidation = "No",
        P.Investigation = "No",
        P.Medicine = "No",
        P.Nature = "No",
        P.Perception = "No",
        P.Performance = "Yes",
        P.Persuasion = "Yes",
        P.Religion = "No",
        P.SleightOfHand = "No",
        P.Stealth = "Yes",
        P.Survival = "No",
        Gender = "Male",
        Age = 22,
        Height = 6 * 0.3048,
        Weight = 190 * 0.453592,
        Eyes = "Cat like",
        Hair = "Black",
        Size = "M",
        Vision = "Darkvision",
        Language1 = "Common",
        Language2 = "Infernal",
        Language3 = NA,
        Language4 = NA,
        Language5 = NA,
        Language6 = NA,
        Alignment = "CG",
        Background = "Entretainer,(actor, storyteller, instrumentalist).
Naci en un pueblo pequeño de humanos.  Al nacer tiefling, mis padres tuvieron muchos problemas para poder sacar nuestra familia adelante, todo el mundo los criticaba y temia, mi padre herrero de tradicion familiar perdio su trabajo y nuestra familia cayo en la pobreza. A mis 5 años mis padres y hermano menor fueron consumidos por la enfermedad que asolo mi pueblo y quede huerfano. SIn tener a donde ir, escapando de las miradas de odio y miedo de la gente de mi pueblo natal, hui de el y comenze a vagar entre pueblos y ciudades sin detenerme, solo y sobreviviendo de aquello que podia robar de los despojos de la gente. 
Pocos meses despues, hambriento y perdido me encontro una caravana de artistas bardos, tambien rechazados de sus propias familias o clanes y me adoptaron como parte de su familia. Me enseñaron a ser actor, a tocar instrumentos y contar las historias de como se creo el universo y los mitos populares. A los 11 desarolle la habilidad de ser bardo y me fueron inculcadas todas mis habilidades, viviendo como nomadas y brindandole a la gente risas y felicidad. Pasaron los años y nuestros lazos fueron haciendose mas y mas fuertes como si fueran ellos mi unica familia. 
",
        RacialTraits = "Intelligence +1, Charisma +2 
Darkvision
Hellish resistance: resist fire
Traumaturgy cantrip
Lvl3: hellish rebuke spell once per day as a 2nd-level spell.
5th level:  you can also cast the darkness spell
once per day.
Charisma is your spellcasting ability for
these spells.",
        PersonalityTraits = "I know a story relevant to almost every situation, also, Whenever I come to a new place, I collect local rumors. Knowledge is power. ",
        Ideals = "People. Our troop performs and figth evil in order to prevent more families to be riped apart. I do not want for anyone to have the pasts that we had. ",
        Bonds = "I would do anything for the other members of my
old troupe, even revenge. ",
        Flaws = "I have a weakness for the poeple who can't defend themselves, i can t harm them, I must protect them.",
        ArmourProficiencies = "Light armor",
        WeaponProficiencies = "Simple weapons, hand crossbows,
longswords, rapiers, shortswords",
        ToolProficienices = "Disguise kit, four  type of musical instruments 
(lute, bombarde, bodhran, bagpipe)
",
        CPieces = 0,
        SPieces = 0,
        EPieces = 0,
        GPieces = 29,
        PPieces = 0,
        SpellSaveDC = 14,
        SpellAttackMod = 6,
        Cantrip1 = "Thaumaturgy",
        Cantrip2 = "Vicious mockery",
        Cantrip3 = "Blade ward",
        Cantrip4 = NA,
        Cantrip5 = NA,
        SpellSlotUsed1 = 0,
        SpellSlotMax1 = 2,
        SpellSlotUsed2 = NA,
        SpellSlotMax2 = NA,
        SpellSlotUsed3 = NA,
        SpellSlotMax3 = NA,
        SpellSlotUsed4 = NA,
        SpellSlotMax4 = NA,
        SpellSlotUsed5 = NA,
        SpellSlotMax5 = NA,
        SpellSlotUsed6 = NA,
        SpellSlotMax6 = NA,
        SpellSlotUsed7 = NA,
        SpellSlotMax7 = NA,
        SpellSlotUsed8 = NA,
        SpellSlotMax8 = NA,
        SpellSlotUsed9 = NA,
        SpellSlotMax9 = NA
    ),
    Krushk = data.frame(
        Name = "Krushk",
        Race = "Half-orc",
        Class = "Bard",
        Str = 20,
        Dex = 14,
        Con = 18,
        Int = 13,
        Wis = 12,
        Cha = 14,
        P.Str = FALSE,
        P.Dex = TRUE,
        P.Con = FALSE,
        P.Int = FALSE,
        P.Wis = FALSE,
        P.Char = TRUE,
        MaxHP = 12,
        Speed = 30,
        AC = 5,
        ACunarmoured = 12,
        Lvl = 1,
        ProfBonus = 2,
        XP = 104,
        P.Acrobatics = "Yes",
        P.AnimalHandling = "No",
        P.Arcana = "No",
        P.Athletics = "Yes",
        P.Deception = "No",
        P.History = "No",
        P.Insight = "No",
        P.Intimidation = "Yes",
        P.Investigation = "No",
        P.Medicine = "No",
        P.Nature = "No",
        P.Perception = "Yes",
        P.Performance = "Yes",
        P.Persuasion = "Yes",
        P.Religion = "No",
        P.SleightOfHand = "No",
        P.Stealth = "No",
        P.Survival = "No",
        Gender = "Male",
        Age = 36,
        Height = 6 * 0.3048,
        Weight = 120,
        Eyes = "Black",
        Hair = "Bald",
        Size = "M",
        Vision = "Darkvision",
        Language1 = "Common",
        Language2 = "Orcish",
        Language3 = NA,
        Language4 = NA,
        Language5 = NA,
        Language6 = NA,
        Alignment = "CN",
        Background = "entreteiner (instrumentalis)",
        RacialTraits = "Darkvision
Menacing (proficiency intimidate)",
        PersonalityTraits = "-tengo un chiste para cada ocasión, sobre todo en momentos inapropiados
-Aprecio el sutil arte de insultar al prójimo",
        Ideals = "debo limpiar al mundo de monstruos para que nadie sufra lo que nosotros",
        Bonds = "-mi grupo pelea contra el mal por venganza, esperando el día en que matemos al dragón rojo que se comió a nuestros amigos.",
        Flaws = "",
        ArmourProficiencies = "light armor",
        WeaponProficiencies = "simple weapons
hand crossbow
longsword
rapiers
shortsword",
        ToolProficienices = "triangulo
harmonica
flauta
disguise kit
banjo",
        CPieces = 0,
        SPieces = 0,
        EPieces = 0,
        GPieces = 20,
        PPieces = 0,
        SpellSaveDC = 12,
        SpellAttackMod = 4,
        Cantrip1 = "True strike",
        Cantrip2 = "Vicious mockery",
        Cantrip3 = NA,
        Cantrip4 = NA,
        Cantrip5 = NA,
        SpellSlotUsed1 = 0,
        SpellSlotMax1 = 2,
        SpellSlotUsed2 = NA,
        SpellSlotMax2 = NA,
        SpellSlotUsed3 = NA,
        SpellSlotMax3 = NA,
        SpellSlotUsed4 = NA,
        SpellSlotMax4 = NA,
        SpellSlotUsed5 = NA,
        SpellSlotMax5 = NA,
        SpellSlotUsed6 = NA,
        SpellSlotMax6 = NA,
        SpellSlotUsed7 = NA,
        SpellSlotMax7 = NA,
        SpellSlotUsed8 = NA,
        SpellSlotMax8 = NA,
        SpellSlotUsed9 = NA,
        SpellSlotMax9 = NA
    ),
    Ky = data.frame(
        Name = "Ky",
        Race = "Wood elf",
        Class = "Rogue",
        Str = 11,
        Dex = 17,
        Con = 14,
        Int = 14,
        Wis = 16,
        Cha = 11,
        P.Str = FALSE,
        P.Dex = FALSE,
        P.Con = FALSE,
        P.Int = FALSE,
        P.Wis = FALSE,
        P.Char = FALSE,
        MaxHP = 10,
        Speed = 35,
        AC = 14,
        ACunarmoured = 13,
        Lvl = 1,
        ProfBonus = 2,
        XP = 104,
        P.Acrobatics = "Yes",
        P.AnimalHandling = "No",
        P.Arcana = "No",
        P.Athletics = "No",
        P.Deception = "No",
        P.History = "Yes",
        P.Insight = "No",
        P.Intimidation = "No",
        P.Investigation = "Expertise",
        P.Medicine = "No",
        P.Nature = "No",
        P.Perception = "Yes",
        P.Performance = "No",
        P.Persuasion = "Yes",
        P.Religion = "No",
        P.SleightOfHand = "Yes",
        P.Stealth = "Expertise",
        P.Survival = "No",
        Gender = "Female",
        Age = 50,
        Height = 6 * 0.3048,
        Weight = 110 * 0.453592,
        Eyes = "Blue",
        Hair = "White",
        Size = "M",
        Vision = "Darkvision",
        Language1 = "Common",
        Language2 = "Elvish",
        Language3 = "Draconic",
        Language4 = NA,
        Language5 = NA,
        Language6 = NA,
        Alignment = "CG",
        Background = "Noble",
        RacialTraits = "Dark Vision, Fey Ancestry, Mask of the Wild, ",
        PersonalityTraits = "Despite my noble birth, I do not place myself above other folk. We all have the same blood.",
        Ideals = "Independence. I must prove that I can handle myself without the coddling of my family.",
        Bonds = "Being the grandchild of a renowned dragon slayer is usually a good way to impress people, but just last week a gang of ruffians attack you. You barely escaped with your life, but as you fled, the ruffians told you that the Cult of the Dragon never forgets and always avenges. You're hoping to lie low in a sleepy town called Greenest until this blows over.",
        Flaws = "By my words and actions, I often bring shame to
my family.",
        ArmourProficiencies = "Light armor",
        WeaponProficiencies = "Longsword, shortsword, shortbow, longbow, simple weapons, hand crossbows, rapiers",
        ToolProficienices = "Dragonchess, thieve's tools",
        CPieces = 0,
        SPieces = 0,
        EPieces = 0,
        GPieces = 40,
        PPieces = 0,
        SpellSaveDC = NA,
        SpellAttackMod = NA,
        Cantrip1 = NA,
        Cantrip2 = NA,
        Cantrip3 = NA,
        Cantrip4 = NA,
        Cantrip5 = NA,
        SpellSlotUsed1 = NA,
        SpellSlotMax1 = NA,
        SpellSlotUsed2 = NA,
        SpellSlotMax2 = NA,
        SpellSlotUsed3 = NA,
        SpellSlotMax3 = NA,
        SpellSlotUsed4 = NA,
        SpellSlotMax4 = NA,
        SpellSlotUsed5 = NA,
        SpellSlotMax5 = NA,
        SpellSlotUsed6 = NA,
        SpellSlotMax6 = NA,
        SpellSlotUsed7 = NA,
        SpellSlotMax7 = NA,
        SpellSlotUsed8 = NA,
        SpellSlotMax8 = NA,
        SpellSlotUsed9 = NA,
        SpellSlotMax9 = NA
    ),
    Lied = data.frame(
        Name = "Lied",
        Race = "Human",
        Class = "Paladin",
        Str = 14,
        Dex = 13,
        Con = 13,
        Int = 9,
        Wis = 12,
        Cha = 15,
        P.Str = FALSE,
        P.Dex = FALSE,
        P.Con = FALSE,
        P.Int = FALSE,
        P.Wis = FALSE,
        P.Char = FALSE,
        MaxHP = 11,
        Speed = 30,
        AC = 19,
        ACunarmoured = 11,
        Lvl = 1,
        ProfBonus = 2,
        XP = 104,
        P.Acrobatics = "No",
        P.AnimalHandling = "No",
        P.Arcana = "No",
        P.Athletics = "No",
        P.Deception = "No",
        P.History = "Yes",
        P.Insight = "Yes",
        P.Intimidation = "Yes",
        P.Investigation = "No",
        P.Medicine = "No",
        P.Nature = "No",
        P.Perception = "No",
        P.Performance = "Yes",
        P.Persuasion = "Yes",
        P.Religion = "Yes",
        P.SleightOfHand = "No",
        P.Stealth = "No",
        P.Survival = "No",
        Gender = "Male",
        Age = 17,
        Height = 1.60,
        Weight = 57,
        Eyes = "Blue",
        Hair = "Blonde",
        Size = "M",
        Vision = "Normal",
        Language1 = "Common",
        Language2 = "Elvish",
        Language3 = "Celestial",
        Language4 = NA,
        Language5 = NA,
        Language6 = NA,
        Alignment = "LG",
        Background = "Noble",
        RacialTraits = "Skill Proficiencies: History, Persuasion
Tool Proficiencies: One type of gaming set Languages: One of your choice
Equipment: A set of fine clothes, a signet ring, a scroll of pedigree, and a purse containing 25 gp",
        PersonalityTraits = "Despite my noble birth, I do not place myself above other folk. We all have the same blood.

My eloquent flattery makes everyone Italk to feel
like the most wonderful and important person in the world.",
        Ideals = "Greater Good. Our lot is to lay down our lives in
defense of others.",
        Bonds = "I must save my sister

Every five nights , you have a strange sequence of apocalyptic dreams . The world is destroyed by cold , chokingfumes,
lightning storms , waves of acid , and horrible fire. Each time , the dream ends with ten evil eyes glaring at you  from the darkness . You feel a strange compulsion to travel to Greenest . Perhaps the answer to the riddle of your dreams
await s you there or your sister.",
        Flaws = "I obey the law, even if the law causes misery.",
        ArmourProficiencies = "All armor. shield",
        WeaponProficiencies = "Simple weapons, martial weapons",
        ToolProficienices = "none",
        CPieces = 0,
        SPieces = 0,
        EPieces = 0,
        GPieces = 40,
        PPieces = 0,
        SpellSaveDC = NA,
        SpellAttackMod = NA,
        Cantrip1 = NA,
        Cantrip2 = NA,
        Cantrip3 = NA,
        Cantrip4 = NA,
        Cantrip5 = NA,
        SpellSlotUsed1 = NA,
        SpellSlotMax1 = NA,
        SpellSlotUsed2 = NA,
        SpellSlotMax2 = NA,
        SpellSlotUsed3 = NA,
        SpellSlotMax3 = NA,
        SpellSlotUsed4 = NA,
        SpellSlotMax4 = NA,
        SpellSlotUsed5 = NA,
        SpellSlotMax5 = NA,
        SpellSlotUsed6 = NA,
        SpellSlotMax6 = NA,
        SpellSlotUsed7 = NA,
        SpellSlotMax7 = NA,
        SpellSlotUsed8 = NA,
        SpellSlotMax8 = NA,
        SpellSlotUsed9 = NA,
        SpellSlotMax9 = NA
    ),
    Macareno = data.frame(
        Name = "Macareno Nyx",
        Race = "Forest Gnome",
        Class = "Wizard",
        Str = 8,
        Dex = 15,
        Con = 13,
        Int = 17,
        Wis = 12,
        Cha = 11,
        P.Str = FALSE,
        P.Dex = FALSE,
        P.Con = FALSE,
        P.Int = TRUE,
        P.Wis = TRUE,
        P.Char = FALSE,
        MaxHP = 7,
        Speed = 30,
        AC = 0,
        ACunarmoured = 12,
        Lvl = 1,
        ProfBonus = 2,
        XP = 104,
        P.Acrobatics = "No",
        P.AnimalHandling = "No",
        P.Arcana = "Yes",
        P.Athletics = "No",
        P.Deception = "No",
        P.History = "No",
        P.Insight = "No",
        P.Intimidation = "No",
        P.Investigation = "Yes",
        P.Medicine = "No",
        P.Nature = "No",
        P.Perception = "No",
        P.Performance = "No",
        P.Persuasion = "No",
        P.Religion = "No",
        P.SleightOfHand = "Yes",
        P.Stealth = "Yes",
        P.Survival = "No",
        Gender = "Male",
        Age = 28,
        Height = 0.9906,
        Weight = 35 * 0.453592,
        Eyes = "Black",
        Hair = "Black",
        Size = "S",
        Vision = "Darkvision",
        Language1 = "Gnomish",
        Language2 = "Common",
        Language3 = "Draconic",
        Language4 = NA,
        Language5 = NA,
        Language6 = NA,
        Alignment = "CN",
        Background = "",
        RacialTraits = "Speak with SmallBeasts. Through sounds and gestures, you can communicate simple ideas with Small or smaller beasts. Forest gnomes love animals and often keep squirrels, badgers, rabbits, moles, woodpeckers, and other creatures as beloved pets.
",
        PersonalityTraits = "I sleep with my back to a wall or tree, with everything I own wrapped in a bundle in my arms.",
        Ideals = "I help the people who help me— that’s what keeps us alive. (Neutral)",
        Bonds = "Every five nights, you have a strange sequence of apocalyptic dream s. The world is destroyed by cold, choking fum es, lightning storm s, waves of acid, and horrible fire. Each time, the dream ends with ten evil eyes glaring at you from the darkness. You feel a strange com pulsion to travel to Greenest. Perhaps the answer to the riddle ofyour dreams awaits you there.",
        Flaws = "People who can't take care of themselves get what they deserve.",
        ArmourProficiencies = "",
        WeaponProficiencies = "Daggers, darts, slings, quarterstaffs, light crossbows.",
        ToolProficienices = "Disguise kit, thieves’ tools ",
        CPieces = 0,
        SPieces = 0,
        EPieces = 0,
        GPieces = 20,
        PPieces = 0,
        SpellSaveDC = 13,
        SpellAttackMod = 5,
        Cantrip1 = "Fire bolt",
        Cantrip2 = "Sacred flame",
        Cantrip3 = NA,
        Cantrip4 = NA,
        Cantrip5 = NA,
        SpellSlotUsed1 = 0,
        SpellSlotMax1 = 2,
        SpellSlotUsed2 = NA,
        SpellSlotMax2 = NA,
        SpellSlotUsed3 = NA,
        SpellSlotMax3 = NA,
        SpellSlotUsed4 = NA,
        SpellSlotMax4 = NA,
        SpellSlotUsed5 = NA,
        SpellSlotMax5 = NA,
        SpellSlotUsed6 = NA,
        SpellSlotMax6 = NA,
        SpellSlotUsed7 = NA,
        SpellSlotMax7 = NA,
        SpellSlotUsed8 = NA,
        SpellSlotMax8 = NA,
        SpellSlotUsed9 = NA,
        SpellSlotMax9 = NA
    ),
    Rhogar = data.frame(
        Name = "Rhogar",
        Race = "Dragonborn",
        Class = "Bard",
        Str = 8,
        Dex = 15,
        Con = 14,
        Int = 14,
        Wis = 10,
        Cha = 19,
        P.Str = FALSE,
        P.Dex = TRUE,
        P.Con = FALSE,
        P.Int = FALSE,
        P.Wis = FALSE,
        P.Char = TRUE,
        MaxHP = 10,
        Speed = 30,
        AC = 13,
        ACunarmoured = 12,
        Lvl = 1,
        ProfBonus = 2,
        XP = 104,
        P.Acrobatics = "Yes",
        P.AnimalHandling = "No",
        P.Arcana = "No",
        P.Athletics = "No",
        P.Deception = "No",
        P.History = "No",
        P.Insight = "No",
        P.Intimidation = "Yes",
        P.Investigation = "No",
        P.Medicine = "No",
        P.Nature = "No",
        P.Perception = "No",
        P.Performance = "Yes",
        P.Persuasion = "Yes",
        P.Religion = "No",
        P.SleightOfHand = "Yes",
        P.Stealth = "No",
        P.Survival = "No",
        Gender = "Male",
        Age = 24,
        Height = 6 * 0.3048,
        Weight = 210 * 0.453592,
        Eyes = "Red",
        Hair = "Green scales",
        Size = "M",
        Vision = "Normal",
        Language1 = "Common",
        Language2 = "Draconic",
        Language3 = NA,
        Language4 = NA,
        Language5 = NA,
        Language6 = NA,
        Alignment = "CN",
        Background = "Entretainer,(actor, fire eater, instrumentalist).",
        RacialTraits = "-D r a c o n i c A n c e s t r y
Green Poison 15 ft. cone (Con. save)
-Breath Weapon.
-Damage Resistance.",
        PersonalityTraits = "-I know a story relevant to almost every situation.
-Whenever I come to a new place, I collect local rumors
and spread gossip.",
        Ideals = "Creativity. The world is in need of new ideas and bold action. (Chaotic)",
        Bonds = "My instrument is my most treasured possession, and it reminds me of someone I love my lost friends of the troupe seeking revenge for them.",
        Flaws = "I have trouble keeping my true feelings hidden. My
sharp tongue lands me in trouble.",
        ArmourProficiencies = "Light armor",
        WeaponProficiencies = "Simple weapons, hand crossbows,
longswords, rapiers, shortswords",
        ToolProficienices = "- aulos 
- lute 
- electric triangle 
-disguise kit 
-drums ",
        CPieces = 0,
        SPieces = 0,
        EPieces = 0,
        GPieces = 13,
        PPieces = 0,
        SpellSaveDC = 14,
        SpellAttackMod = 6,
        Cantrip1 = "Vicious mockery",
        Cantrip2 = "Message",
        Cantrip3 = NA,
        Cantrip4 = NA,
        Cantrip5 = NA,
        SpellSlotUsed1 = 0,
        SpellSlotMax1 = 2,
        SpellSlotUsed2 = NA,
        SpellSlotMax2 = NA,
        SpellSlotUsed3 = NA,
        SpellSlotMax3 = NA,
        SpellSlotUsed4 = NA,
        SpellSlotMax4 = NA,
        SpellSlotUsed5 = NA,
        SpellSlotMax5 = NA,
        SpellSlotUsed6 = NA,
        SpellSlotMax6 = NA,
        SpellSlotUsed7 = NA,
        SpellSlotMax7 = NA,
        SpellSlotUsed8 = NA,
        SpellSlotMax8 = NA,
        SpellSlotUsed9 = NA,
        SpellSlotMax9 = NA
    ),
    Sariel = data.frame(
        Name = "Sariel Meliamne (Oakenhell)",
        Race = "Wood elf",
        Class = "Cleric",
        Str = 13,
        Dex = 12,
        Con = 14,
        Int = 13,
        Wis = 15,
        Cha = 10,
        P.Str = FALSE,
        P.Dex = FALSE,
        P.Con = FALSE,
        P.Int = FALSE,
        P.Wis = TRUE,
        P.Char = TRUE,
        MaxHP = 10,
        Speed = 35,
        AC = 18,
        ACunarmoured = 11,
        Lvl = 1,
        ProfBonus = 2,
        XP = 104,
        P.Acrobatics = "No",
        P.AnimalHandling = "No",
        P.Arcana = "No",
        P.Athletics = "No",
        P.Deception = "No",
        P.History = "No",
        P.Insight = "Yes",
        P.Intimidation = "No",
        P.Investigation = "No",
        P.Medicine = "Yes",
        P.Nature = "No",
        P.Perception = "Yes",
        P.Performance = "No",
        P.Persuasion = "Yes",
        P.Religion = "Yes",
        P.SleightOfHand = "No",
        P.Stealth = "No",
        P.Survival = "No",
        Gender = "Female",
        Age = 200,
        Height = 1.6256,
        Weight = 110 * 0.453592,
        Eyes = "Violet",
        Hair = "Golden",
        Size = "M",
        Vision = "Darkvision",
        Language1 = "Common",
        Language2 = "Elvish",
        Language3 = "Orcish",
        Language4 = "Gnomish",
        Language5 = NA,
        Language6 = NA,
        Alignment = "NG",
        Background = "Acolyte. Selûne Godess of moon. ",
        RacialTraits = "- Your Dexterity score+ 2.
-Wisdom +1 
-Fleet of foot 35ft speed.
-Mask of the wild: can attempt to hide even when you are only in obscure foliage, heavy rain, falling snow, mist ...
 -Age. Adult- 100 and can live to be 750 years . -Darkvision. you have superior vision in dark and dim conditions. 
-Keen Senses. You have proficiency in the Perception skill. 
-Fey Ancestry. You have advantage on saving throws against being charmed, and magic can’t put you to sleep. 
-Trance. Elves don’t need to sleep. meditate deeply, for 4 hours a day.  
-Languages. Common and Elvish.",
        PersonalityTraits = "I am tolerant of other faiths and respect the worship of other gods, also i try to prevent inesesary violence, almost everithing can be arranged talking ",
        Ideals = "i trust that my deity will guide my action. I have faith that if i work hard, things will go well. ",
        Bonds = "i will do anything to protect the temple where i served. ",
        Flaws = "I am suspicious of strangers and expect the worst of them. ",
        ArmourProficiencies = "light armor, medium armor, shields, heavy armor.",
        WeaponProficiencies = "longsword, shortsword, shortbow, longbow, all simple weapons",
        ToolProficienices = "",
        CPieces = 0,
        SPieces = 0,
        EPieces = 0,
        GPieces = 24,
        PPieces = 0,
        SpellSaveDC = 12,
        SpellAttackMod = 4,
        Cantrip1 = "Light",
        Cantrip2 = "Spare the dying",
        Cantrip3 = "Sacred flame",
        Cantrip4 = NA,
        Cantrip5 = NA,
        SpellSlotUsed1 = 0,
        SpellSlotMax1 = 2,
        SpellSlotUsed2 = NA,
        SpellSlotMax2 = NA,
        SpellSlotUsed3 = NA,
        SpellSlotMax3 = NA,
        SpellSlotUsed4 = NA,
        SpellSlotMax4 = NA,
        SpellSlotUsed5 = NA,
        SpellSlotMax5 = NA,
        SpellSlotUsed6 = NA,
        SpellSlotMax6 = NA,
        SpellSlotUsed7 = NA,
        SpellSlotMax7 = NA,
        SpellSlotUsed8 = NA,
        SpellSlotMax8 = NA,
        SpellSlotUsed9 = NA,
        SpellSlotMax9 = NA
    )
)
```

```{r 'processChars', echo = FALSE, warning = FALSE}
## Process the characters
chars.wide <- do.call(rbind, lapply(chars.raw, processChar))
chars.wide$Character <- names(chars.raw)

## Convert to long format
library('reshape2')
chars.long <- melt(chars.wide, id.vars = "Character", na.rm = TRUE)
chars.long$variable <- as.character(chars.long$variable)

## Fix some column names
chars.long$variable[grepl("Language", chars.long$variable)] <- "Language"
chars.long$variable[grepl("Cantrip", chars.long$variable)] <- "Cantrip"

## Sort
chars <- chars.long[order(chars.long$variable), ]
```



# Browse data

Select one or more variables to view.

```{r 'browseLong', echo=FALSE}
inputPanel(
    selectInput("var", label = "Variable of interest", choices = unique(chars$variable), selected = "Wealth", multiple = TRUE)
)

renderDataTable(
    subset(chars, variable %in% input$var),
    options = list(iDisplayLength = 25),
)
```

Some nomenclature used:

* Wealth: Coins converted to GP.
* Height: in meters.
* Weight: in kilograms.
* P.Str, P.Dex, ..., P.Cha represent whether the character has a saving proficiency.
* P.Athletics, ..., P.Survival show whether the character is proficient, expert, or not proficient in that skill.

# Armour

Maximum AC (armoured vs unarmoured) for each character

```{r 'armour', echo=FALSE}
d <- subset(chars, variable %in% c("AC", "ACunarmoured"))
d <- d[order(d$Character), ]
i <- tapply(d$value, d$Character, which.max)
i[2:length(i)] <- i[2:length(i)] + cumsum(rep(2, length(i) -1))
AC <- d[i, ]

renderDataTable(
    AC
)

```

# Export data

```{r 'export'}
save(chars, file = "chars.Rdata")
```


# Reproducibility

Date generated

```{r 'date', echo = FALSE}
Sys.time()
```

R Session information

```{r 'sessionInfo', echo = FALSE}
sessionInfo()
```

Created as an [interactive document](http://rmarkdown.rstudio.com/authoring_shiny.html) using [RStudio](http://www.rstudio.com/).

Code available via GitHub [here](https://github.com/lcolladotor/DnD5e-HotDQ-chars).

